A fully labelled proof system for intuitionistic modal logics

### 2019-09-26 caleidoscope/caleidoscope.tex
switched soundness and completeness
done with completeness

@@

\todo{an introduction? do not repeat the theorem?}
\begin{theorem}
	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
\end{theorem}

\begin{proof}
	In order to prove completeness, we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necessitation rule and modus ponens.

	As we mentioned, in the course of the proof, we have to derive the five $\kax$ axioms. In the derivation of $\kax[1]$ is illustrated the need of having the rules corresponding to $\rn{refl}$ and $\rn{trans}$ in the system:

		\begin{center}
			$\vlderivation{
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
				{\vlin {\rlabrn{\IMP}}
					{\lb z \mbox{ fresh}}
					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
					{\vlin {\rlabrn{\BOX}}
						{\lb w, \lb u \mbox{ fresh}}
						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
						{\vlin {\llabrn{\BOX}}
							{}
							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
							{\vlin {\color{red}\rn{trans}}
								{}
								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
								{\vlin {\llabrn{\BOX}}
									{}
									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
									{\vlin {\color{red}\rn{refl}}
										{}
										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
										{\vliin{\llabrn{\IMP}}
											{}
											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
											{\vlin {\rn{id}}
												{}
												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
												{\vlhy {}}}
											{\vlin {\rn{id}}
												{}
												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
												{\vlhy {}}}}}}}}}}
			}$
		\end{center}

		where $G$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.

	%%%
	We can also show that the rule $\rn{refl}$ is needed in the derivation of $\kax[2]$:

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
		{\vlin {\rlabrn{\IMP}}
			{\lb z \mbox{ fresh}}
			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
				{\vlin{\rlabrn{\DIA}}
					{}
					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
					{\vlin {\llabrn{\BOX}}
						{}
						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
						{\vlin {\color{red}\rn{refl}}
							{}
							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
							{\vliin{\llabrn{\IMP}}
								{}
								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
								{\vlin {\rn{id}}
									{}
									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
									{\vlhy {}}}
								{\vlin {\rn{id}}
									{}
									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
									{\vlhy {}}}								}}}}}}
	}$
\end{center}

where $T$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.

	%%%%
	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$: %which also illustrates the need of having the rule corresponding to $\rn{refl}$:

	\begin{center}

		$\vlderivation {
			\vlin{\rlabrn{\IMP}}
			{}
			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{}
				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
									{\vlhy {}}}}}}}}
		}$

The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame condition $\rn{F_1}$:

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
		{\vlin {\rlabrn{\BOX}}
			{\lb z, \lb w \mbox{ fresh}}
			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
			{\vlin {\rlabrn{\IMP}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
				{\vlin {\color{red}{\rn{F_1}}}
					{}
					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
					{\vlin {\rn{trans}}
						{}
						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
						{\vliin {\llabrn{\IMP}}
							{}
							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
							{\vlin {\rlabrn{\DIA}}
									{}
									{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
									{\vlin {\rn{refl}}
										{}
										{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
										{\vlin {\rn{id}}
											{}
											{R, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
											{\vlhy {}}}}}
							{\vlin {\rn{refl}}
								{}
								{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
								{\vlin {\llabrn{\BOX}}
									{}
									{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
									{\vlin {\rn{refl}}
										{}
										{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
										{\vlin {\rn{id}}
											{}
											{R, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
											{\vlhy {}}}}}}}}}}}
	}$

where $R$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.

To complete the proof of the five variants of $\kax$ we still have to see that we can prove $\kax[5]$:

\begin{center}

	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
		{\vlin {\llabrn{\DIA}}
			{}
			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
			{\vlin {\llabrn{\BOT}}
				{}
				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
				{\vlhy {}}}}
	}$

As we mentioned, in the course of the proof of the theorem, we have to give a proof for all the axioms of propositional intuitionistic logic. As an example, we display the proof of the axiom $\rn{AND}$-$\rn{2}$: $ \fm{A \AND B \IMP B}$:

\begin{center}
	$\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{A \AND B \IMP B}}
		{\vlin {\llabrn{\AND}}
			{}
			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
			{\vlin {\rn{refl}}
				{}
				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
				{\vlin {\rn{id}}
					{}
					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
					{\vlhy {}}}}}
	}$
\end{center}

\todo{I do not know how to close the theorem}

As we mentioned, in order to conclude the proof of the Theorem~\ref{thm:cutfree-compl} we simulate the necessitation rule and modus ponens.

\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we show our system at work, as most of the section
consists of derivations of axioms of $\IK$ in $\labIKp$. More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:

\begin{theorem}\label{thm:completeness}
	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
\end{theorem}

\begin{remark}
  We have seem already in the proof of Proposition~\ref{prop:id} the
  need of the rule $\rn{F_2}$. In the following proof of
  Theorem~\ref{thm:completeness} we also see the need of the rules
  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
  \begin{itemize}
  \item $\kax[1]$:
    $$
    \vlderivation{
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
				{\vlin {\rlabrn{\IMP}}
					{\lb z \mbox{ fresh}}
					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
					{\vlin {\rlabrn{\BOX}}
						{\lb w, \lb u \mbox{ fresh}}
						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
						{\vlin {\llabrn{\BOX}}
							{}
							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
							{\vlin {\color{red}\rn{trans}}
								{}
								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
								{\vlin {\llabrn{\BOX}}
									{}
									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
									{\vlin {\color{red}\rn{refl}}
										{}
										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
										{\vliin{\llabrn{\IMP}}
											{}
											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
											{\vlin {\rn{id}}
												{}
												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
												{\vlhy {}}}
											{\vlin {\rn{id}}
												{}
												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
												{\vlhy {}}}}}}}}}}
    }
    $$
    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
  \item $\kax[2]$:
    $$
    \vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
		{\vlin {\rlabrn{\IMP}}
			{\lb z \mbox{ fresh}}
			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
				{\vlin{\rlabrn{\DIA}}
					{}
					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
					{\vlin {\llabrn{\BOX}}
						{}
						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
						{\vlin {\color{red}\rn{refl}}
							{}
							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
							{\vliin{\llabrn{\IMP}}
								{}
								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
								{\vlin {\rn{id}}
									{}
									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
									{\vlhy {}}}
								{\vlin {\rn{id}}
									{}
									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
									{\vlhy {}}}								}}}}}}
    }
    $$
    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
  \item $\kax[3]$:
    $$
    \vlderivation {
			\vlin{\rlabrn{\IMP}}
			{}
			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
			{\vlin {\llabrn{\DIA}}
				{}
				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
						{}
						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
						{\vlin {\rlabrn{\DIA}}
							{}
							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
							{\vlin {\rn{refl}}
								{}
								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
								{\vlin {\rn{id}}
									{}
									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
									{\vlhy {}}}}}}}}
		}
    $$
  \item $\kax[4]$:
    $$
\vlderivation {
		\vlin{\rlabrn{\IMP}}
		{\lb y \mbox{ fresh}}
		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
		{\vlin {\rlabrn{\BOX}}
			{\lb z, \lb w \mbox{ fresh}}
			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
			{\vlin {\rlabrn{\IMP}}
				{\lb u \mbox{ fresh}}
				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
				{\vlin {\color{red}{\rn{F_1}}}
					{}
					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
					{\vlin {\rn{trans}}
						{}
						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
						{\vliin {\llabrn{\IMP}}
							{}
							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
							{\vlin {\rlabrn{\DIA}}
									{}
									{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
									{\vlin {\rn{refl}}
										{}
										{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
										{\vlin {\rn{id}}
											{}
											{\B, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
											{\vlhy {}}}}}
							{\vlin {\rn{refl}}
								{}
								{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
								{\vlin {\llabrn{\BOX}}
									{}
									{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
									{\vlin {\rn{refl}}
										{}
										{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
										{\vlin {\rn{id}}
											{}
											{\B, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
											{\vlhy {}}}}}}}}}}}
}
$$
where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
\item $\kax[5]$:
  $$
  \vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
		{\vlin {\llabrn{\DIA}}
			{}
			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
			{\vlin {\llabrn{\BOT}}
				{}
				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
				{\vlhy {}}}}
  }
  $$
  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
  $$
  \vlderivation {
		\vlin{\rlabrn{\IMP}}
		{}
		{\Rightarrow \labels{x}{A \AND B \IMP B}}
		{\vlin {\llabrn{\AND}}
			{}
			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
			{\vlin {\rn{refl}}
				{}
				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
				{\vlin {\rn{id}}
					{}
					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
					{\vlhy {}}}}}
  }
  $$
  Finally, we have to show how the rules of modus ponens and
  necessitation can be simulated in our system. For modus ponens, this
  is standard using the cut rule and for necesitation, we can
  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
  follows:

  \todo{}

  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
\end{proof}

\todo{all refl,trans, \rn{F_2} and $F_1$ in red}

\todo{use the macro for sequents (the macro uses a longer arrow)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
